Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-16 paper/structureScene.tex
Add Andén biography

un important task in computational ecoacoustics is to determine the similarity of two audio scenes. This is often done using bag-of-frames models and other representations based on summary statistics. While these successfully characterize static scenes with little variability in sound content, they are unable to accurately differentiate scenes characterized by a few distinct sound events superimposed over a static background. To address this problem, we propose a two-scale representation, which describes a signal at a short scale using scattering transforms while relying on a cluster model to characterize its larger-scale structure. To motivate this, we validate the use of scattering transforms for supervised acoustic scene classification (ASC), illustrating its state-of-the-art performance compared to traditional feature transforms like mel-frequency cepstral coefficients (MFCCs). Furthermore, we illustrate the power of the full cluster-based representation by applying it to an acoustic scene similarity retrieval (ASSR) task, where we again significantly outperform more traditional approaches based on summary statistics of MFCCs.

@@

% Note that keywords are not normally used for peerreview paper.
\begin{IEEEkeywords}
ecoacoustics, acoustic scene classification, acoustic scene similarity retrieval, cluster models, wavelets, scattering, invariance
\end{IEEEkeywords}

@@

\IEEEPARstart{T}{he} amount of audio data recorded from our sonic environment has grown considerably over the past decades.
In order to measure the effect of human activity and climate change on animal biodiversity researchers have recently undertaken the massive deployment of acoustic sensors throughout the world \cite{warren2006urban, NessSST13, stowell13b}. 
In addition, recent work has explored acoustic monitoring for characterization of human pleasantness in urban areas \cite{guyot2005urban, ricciardi2015sound}, as well as the prediction of annoyance due to traffic \cite{gloaguen}.
Because they bear a strong societal impact and raise many scientific challenges, we believe that these applications are of considerable interest for the signal processing community.

This works falls in the realm of ecoacoustics, which is the interdisciplinary study of relationships between natural or anthropogenic sounds and their environments at the intersection of ecology, acoustics and computer science \cite{krause}. Despite identified needs, the field of signal-based ecoacoustics is still in its infancy.
Consequently, few well-designed datasets are readily available for evaluation purposes.

An important problem in this field is the characterization of auditory scenes for the purposes of similarity estimation. One application of this is acoustic scene similarity retrieval (ASSR), where the scenes judged ``most similar'' to a given query scene are extracted from some larger dataset. This requires the auditory scenes to be represented in some way that captures their distinctive qualities. Often, this has been achieved by bag-of-frames approaches, which attempt to describe the auditory scene recording using summary statistics. Unfortunately, since this only captures the average structure of the scene, the approach often fails when presented scenes which are dynamic and contain rare, distinct sound events that discriminate the scene from others.Indeed, experiments in cognitive psychology suggests that this matches more closely the way that humans and other animals perceive acoustic scenes. \ja{Refs?}

To design better representations for the similarity retrieval task, we draw inspiration from a closely related, and more mature, field of investigation: the classification of acoustic scenes.This task, consisting of predicting scene labels from audio recordings, is narrower in its range of applications, but has the advantage of being rooted in the cognitive psychology of categorization \cite{dubois2006cognitive,guastavino_ideal_2006}. In addition, it has received significant attention from the data mining community for some time, resulting in the availability of well-designed datasets and competitive algorithms for solving it.

The first question to be answered when confronted with this task is how is the signal to be represented at a low level. In other words, how do we represent an extract of the auditory scene signal over a sub-second interval? A standard tool for this are the mel-frequency cepstral coefficients (MFCCs), originally developed for speech processing \cite{davis-mermelstein}, but which have found wider use in recent years \cite{logan}. \ja{Other MFCC works?} A richer set of features are found in the scattering transform, a generic signal representation which has enjoyed significant success in various audio classification tasks \cite{Anden2014}.

The next question is the choice of a classifier. Here, a class of particularly successful algorithms train a classifier, such as a support vector machine (SVM), to discriminate between short extracts of an auditory scene, and at the classification stage divide the signal into short extracts which are classified separately before pooling the classification results to reach a final decision. This last step is known as late integration and is crucial to the success of these methods, since it allows the classifier to concentrate on the short, distinct sound events that discriminate between scenes. The success of the late integration technique again leads credence to the idea that rare, distinct events in an auditory scene are sufficient to characterize it completely. Combining scattering transforms for low-level representation with late-integrated SVMs used for classifying the scene at a higher level, we obtain a competitive auditory scene classification system, demonstrating the usefulness of both concepts for this task.

Returning to scene retrieval setting, we cannot use supervised models such as SVMs, but we can emulate their selection behavior by quantizing the auditory scene and defining a distance over this quantization. We therefore propose a new model for acoustic scenes, where the signal is represented at sub-second scales by scattering transforms, while larger scales are captured by an unsupervised method that quantizes the scattering coefficients into a number of clusters. We then use these to define a set of distances that can subsequently be used for similarity retrieval.Testing this approach on an scene retrieval task, we obtain significant improvements over traditional bag-of-frames and summary statistics models, applied both to MFCCs and scattering coefficients.

@@

%The same division is found in the field of auditory scene analysis, wherein the interest may either be 1) to isolate and identify precise events, \ie acoustic event detection (AED), or 2) to predict global attributes assigned to large time spans of audio, \ie acoustic scene classification (ASC).
For these tasks, a popular approach is the bag-of-frames (BOF) approach for acoustic scene modeling introduced by Aucouturier et al. \cite{aucouturier2007bag}, where a scene is modeled by high-level summary statistics computed from local features.
Interestingly, the proposed implementation using Gaussian mixture models (GMMs) of mel-frequency cepstral coefficients (MFCCs) has been demonstrated to perform comparably to a direct averaging of the features for a variety of tasks \cite{lagrange:hal-01082501}.
This contrasts with the typical morphology of acoustic scenes, which is a ``skeleton of events on a bed of textures'' \cite{nelken2013} where a few discrete sound events superimposed upon a stationary acoustic background.
Therefore, it is arguably more beneficial to focus on characterizing these distinct events through describing the large-scale temporal evolution of auditory scenes rather than on the joint probability distribution of short-term features.

@@

Aside from \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501} that consider the task of ASSR, much of the work dedicated to acoustic scene modeling is applied to the ASC task.
An overview of the efforts for the latter task is provided by the IEEE Audio and Acoustic Signal Processing (AASP) Detection and Classification of Acoustic Scenes and Events (DCASE) challenge \cite{barchiesi2015acoustic}, held in 2013 to compare different approaches to scene classification.

The methods that performed the best all followed a similar structure, where a low-level feature representation, such as MFCCs, were calculated over short windows and fed separately to a classifier, such as an SVM, for training. During the classification stage, the recording to be classified was similarly processed into short windows represented by feature vectors which were classified individually by the classifier and the classifier output was combined over the recording through majority vote. This last step is known as late integration and allows the classifier to work on individual, shorter-scale sound events instead of trying to classify the recording as a whole. By doing this, the classifier is able to identify and exploit the distinct events that characterize the scene instead of trying to model its average structure. This is in agreement with the psychoacoustic results related to the perception of auditory scenes presented above.

@@

\subsection{Invariance and stability in audio signals}
The notion of invariance to time-shifting plays an essential role in acoustic scene similarity retrieval as well as acoustic scene classification.
Indeed, recordings may be shifted locally without affecting their original class memberships.
To discard this superfluous source of variability, signals can be mapped to a time-shifting invariant feature space before training the classifier, eliminating the need for this classifier to explicitly learn this invariance and increasing the robustness of its predictions.

@@

Prior to constructing models (for classification or similarity estimation), it is beneficial to process scattering coefficients to improve invariance, normality, and generalization power.
In this section, we review three transformations which achieve these properties, namely logarithmic compression and standardization.

@@

\section{Supervised classification system}
\label{sec:supervised}

We are now ready to present the supervised method that we will apply to the acoustic scene classification task using scattering transforms. It consists of two parts, a classifier and a temporal integration method. While the classifier is an SVM, we shall consider two integration approaches, early and late.

\subsection{Support vector machine classifier}
\label{sec:svm}

A support vector machine (SVM) is a binary discriminative classifier that attempts to find a separating hyperplane between a pair of classes of that provides the maximal margin between the two sets\cite{cortes-vapnik}. From another point of view, it attemts to find a direction on which to project in order to maximize separation between two point clouds. Since it is not a generative, but discriminative model, it is able to pick out those feature vectors that best characterize a particular class of auditory scenes compared to another. This property, coupled with its ease of use and efficient implementations \cite{libsvm} have rendered SVMs a popular choice for many classification systems.

At the classification stage, the SVM gives a class label as output, which is one of the two classes it models. For multi-class settings, a one-\vs-one approach is often used, where an SVM is trained for each pair of classes. During classification, the outputs of all pairwise SVMs is computed and the class selected the largest number of times is chosen.

@@

A potential drawback of early integration is that it reduces a sequence of feature vectors to a single average. If the underlying signal is static in nature, this may be advantageous, as the temporal variation of the feature vectors constitutes an unwanted source of variability. For many audio signals, and in particular auditory scenes, this is very far from the truth, and prevents us from identifying the distinct sound events that characterize the signal as these may be drowned out by the background during the averaging step. In this case, a late integration approach would perform better, since it operates on the individual feature vectors and only the classification results are aggregated over time. Using experiments in acoustic scene classification below, we will demonstrate that the late integration approach does indeed succeed over early integration when scattering coefficients are used.

\section{Relevance-based quantization of features}
\label{sec:object}

@@

As discussed in Section \ref{sec:soa}, results in sound perception suggest the appropriateness of source-driven representations of auditory scenes for predicting high-level properties. While this can be addressed in the supervised case using late integration of discriminative classifiers (see Section \ref{sec:eili}), this is not possible in the unsupervised case. As the detection of events is still an open problem \cite{7100934}, we consider in this paper a generic quantization scheme in order to identify and represent time intervals of the scene that are coherent, thus likely to be dominated by a given source of interest.

@@

\subsection{Experiment \#1: acoustic scene classification}

Our first task is to compare the performance of the standard scattering transform, the logarithmically compressed scattering (log-scattering) transform, and baseline MFCCs. Secondly, we evaluate the two temporal integration approaches presented above, \emph{early} and \emph{late}.

The different systems are evaluated on the private part of the DCASE 2013 dataset using five-fold stratified cross validation. The folds are identical to those used in the original challenge. The slack parameter $C$ of the SVM is here set to $1$. Both linear and Gaussian RBF kernels are used. For the latter, a local scaling method is applied \cite{selfTuneManor2004}. All feature vectors, that is scattering frames, MFCCs and centroids, are standardized prior to be given to the classifier. The standardization is computed with respect to the train/test splits of the cross validation scheme (see Section \ref{sec:stand}). Optimal parameters (see above) are this time learned on the public part of the DCASE 2013 dataset, also using five-fold stratified cross validation. \ja{Which parameters are these?} For these experiments, both \emph{early} and \emph{late} integration strategies are evaluated (see Section \ref{sec:eili}).

\subsection{Experiment \#2: acoustic scene similarity retrieval}

Having validated the underlying assumptions for the cluster-based auditory scene representation, we evaluate its performance for the task of acoustic scene similarity retrieval.

The evaluation is performed on the private part of the DCASE 2013 dataset. The metric used is the precision at rank $k$ ($p@k$), which is computed by taking a query item and counting the number of items of the same class within the $k$ closest neighbors, and then averaging over all query items. The $p@k$ is computed for $k=\lbrace 1,\ldots,9\rbrace$, since each class only has $10$ items. Note that a $p@1$ is equivalent to the classification accuracy obtained by the classifier which chooses the label of the closest neighbor for a given item. For each experimental setting, we only report the results obtained with the sets of parameters, \emph{i.e.} the number of clusters $M$ for the \emph{ob} approaches and the scaling parameter $q$ of the RBF kernels (see Eq. \ref{eq:kc}) leading to the best $p@9$. The \emph{ob} approaches are compared to commonly used early integration approach \emph{early}. \ja{And BOF?}

@@

The results on acoustic scene classification illustrate the superior performance of the log-scattering transform coupled with late integration, confirming the ideas motivating the construction of our cluster-based auditory scene representation. Using this representation for auditory scene similarity retrieval, we obtain results that improve significantly over traditional BOF and summary approaches, both with log-scattering features and MFCCs.

\subsection{Experiment \#1: acoustic scene classification}

@@

Logarithmic compression provides a small, albeit consistent boost to acoustic scene classification over all folds in the DCASE 2013 private dataset.
Indeed, as discussed in subsection \ref{sec:logcomp}, and observed in Figure \ref{fig:compression}, the statistical assumption of normality for scattering coefficients is only approximately satisfied once mapped to a logarithmic, decibel-like scale. This transformation improves the discriminative power of the SVMs trained on scattering coefficients, regardless of the chosen temporal integration strategy (early or late) and the inner product kernel (linear or Gaussian RBF).

\subsection{Experiment \#2: acoustic scene similarity retrieval}

This section presents evaluation results for the ASSR settings. The $p@k$ for different settings are shown in Figure \ref{fig:ASS_1}, illustrating the effect of the different similarity metrics.

@@

@@

>>>>

This paper introduces a generic hierarchical modeling scheme for acoustic scenes using the wavelet scattering transform at sub-second time-scales with relevance-based quantization at larger time-scales. Instead of representing a scene using summary statistics, a method popularized by bag-of-features models, each scene is represented by a subset of its most representative features, allowing the retrieval system to focus on discriminative features. We demonstrate the potential of the proposed approach for both acoustic scene similarity retrieval and acoustic scene classification tasks on publicly available datasets, consistently outperforming baseline mel-frequency cepstral coefficient (MFCC) methods.

@@

% Note that keywords are not normally used for peerreview paper.
\begin{IEEEkeywords}
acoustic scene classification, acoustic scene segmentation, acoustic scene similarity retrieval, scattering, wavelets, invariance
\end{IEEEkeywords}

@@

\IEEEPARstart{T}{he} amount of audio data recorded from our sonic environment has grown considerably over the past decades.
In order to measure the effect of human activity and climate change on animal biodiversity, researchers in the field of ecoacoustics \cite{krause} have recently undertaken the massive deployment of acoustic sensors throughout the world \cite{warren2006urban, NessSST13, stowell13b}. 
In addition, recent work has explored acoustic monitoring for characterization of human pleasantness in urban areas \cite{guyot2005urban, ricciardi2015sound}, as well as the prediction of annoyance due to traffic \cite{gloaguen}.
Because they bear a strong societal impact and raise many scientific challenges, we believe that these applications are of considerable interest for the signal processing community.

Ecoacoustics is the interdisciplinary study of relationships between natural or anthropogenic sounds and their environments at the intersection of ecology, acoustics and computer science. Despite identified needs, the field of signal-based ecoacoustics is still in its infancy.
As a consequence, few well-designed datasets are readily available for evaluation purposes.

A closely related, and more mature, field of investigation is the classification of acoustic scenes, where the aim is to predict labels by processing audio data.
While narrower in its range of applications, it has the advantage of being rooted in the cognitive psychology of categorization \cite{dubois2006cognitive, guastavino_ideal_2006} and has received the attention of the data mining community for some time, resulting in the availability of well-designed datasets.

Despite the differences, ecoacoustics and acoustic scene classification (ASC) task both raise the following question: how can we efficiently and effectively process a large amount of audio data using representations that are compact, generic in their design, and flexible in their use?
The work described in this paper attempts to answer this question by demonstrating the usefulness of two concepts for environmental audio processing: 1) application of the wavelet scattering transform to extract discriminative features and 2) large time-scale modeling of the acoustic scene based on unsupervised clustering of each acoustic scene, allowing us to focus the scene description on a few salient sound objects that carry most of the semantic information.

@@

%The same division is found in the field of auditory scene analysis, wherein the interest may either be 1) to isolate and identify precise events, \ie acoustic event detection (AED), or 2) to predict global attributes assigned to large time spans of audio, \ie acoustic scene classification (ASC).
For these tasks, a popular approach is the bag-of-frames (BOF) approach for acoustic scene modeling introduced by Aucouturier et al. \cite{aucouturier2007bag}, where a scene is modeled by high-level summary statistics computed from local features.
Being a very generic method, this approach has been applied to many audio classification tasks besides ASC.
Yet the proposed implementation using Gaussian mixture models (GMMs) of mel-frequency cepstral coefficients (MFCCs) has been demonstrated to perform comparably to a direct averaging of the features for a variety of tasks \cite{lagrange:hal-01082501}.
Indeed, the typical morphology of acoustic scenes is a ``skeleton of events on a bed of textures'' \cite{nelken2013}, with a few discrete sound events superimposed upon a stationary acoustic background.
Therefore, it is arguably more beneficial to focus on characterizing these distinct events through describing the large-scale temporal evolution of auditory scenes rather than on the joint probability distribution of short-term features.

@@

Aside from \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501} that consider the task of ASSR, much of the work dedicated to acoustic scene modeling is applied to the ASC task.
An overview of the efforts for the latter task is provided by the IEEE Audio and Acoustic Signal Processing (AASP) Detection and Classification of Acoustic Scenes and Events (DCASE) challenge \cite{barchiesi2015acoustic}, held in 2013 to compare different approaches to scene classification. Table \ref{tab:dcase} summarizes the results of the submitted algorithms as well as newer systems that use the private part of the DCASE 2013 dataset for their experiments. Most of the scene prediction results are achieved by majority voting of predictions over local features.

\begin{table}
\begin{center}
\caption{Algorithms evaluated on the DCASE 2013 private dataset of acoustic scene classification. Algorithms above the horizontal line participated to the DCASE challenge. The algorithm marked with $^*$ considered only the public dataset. \label{tab:dcase} \ml{need to define RQA ILD LDA or remove table ?} 
}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\hline
\cite{olivetti2013wonder} & 17 & compression distance, random forests \\
\cite{elizalde2013vector} & 55 & i-vector, LDA \\
\cite{krijnders2013tone} & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} & 60 & unsupervised learning over mel spectra, SVMs \\
\cite{nogueira2013sound} & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} & 69 & mel spectra and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} & 69 & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} & 72 & MFCCs, tree baggers \\
\cite{roma2013} & 76 & RQA features stacked with MFCCs, SVMs \\
\hline
\cite{phan2016label} & 84/87 & label tree embedding of Gammatone, SVMs \\
\cite{7362846} & 85$^*$ & amplitude modulated spectra, LDA \\
\end{tabular}
\end{center}
\end{table}

@@

\subsection{Invariance and stability in acoustic scenes}
The notion of invariance to time-shifting plays an essential role in acoustic scene similarity retrieval as well as acoustic scene classification.
Indeed, recordings may be shifted locally without affecting their original class memberships.
To discard this superfluous source of variability, signals can be mapped to a time-shifting invariant feature space before training the classifier, eliminating the need for this classifier to explicitly learn this invariance and increasing the robustness of its predictions.

@@

Before classification or clustering, it is beneficial to process scattering coefficients to improve invariance, normality, and generalization power.
In this section, we review three transformations which achieve these properties, namely logarithmic compression, temporal integration, and standardization.

@@

@@

A drawback of early integration is that it drastically reduces the number of training instances at the classifier stage, down to one per auditory scene.
In the context of the DCASE 2013 private dataset, this corresponds to merely $8$ training instances per class, and $80$ instances overall, which can increase the variance of the estimated model and run the risk of overfitting.
On the contrary, once the scattering representation $\mathbf{S}\boldsymbol{x}(t,\gamma)$ has been unpadded of any boundary artifacts, a late integration scheme for $T=372\textrm{ ms}$ would yield $128$ instances per $30$-second auditory scene, resulting in $10240$ instances overall.
However, many of these instances may be silent or lack any salient properties of the class they are assigned to, which may increase the bias in the estimated model and run the risk of underfitting.
Moreover, when applying late integration, the classifier optimizes accuracy at the frame level, not at the scene level, so its prediction might not yield optimal training error under the final evaluation metric.
In short, early and late integration methods lie at opposite ends of the bias-versus-variance statistical tradeoff. The appropriateness of either approach depends therefore on the nature of the signal that is classified.
We refer to \cite{Joder2009} for a comprehensive review of this problematic in the context of musical instrument recognition.
In the context of this paper, early integration refers to an averaging of the features and late integration refers to a majority vote of the predictions given by an SVM.

\section{Relevance based quantization of features}
\label{sec:object}

@@

As discussed in Section \ref{sec:soa}, results in sound perception suggest the appropriateness of source-driven representations of auditory scenes for predicting high-level properties. As the detection of events is still an open problem \cite{7100934}, we consider in this paper a generic quantization scheme in order to identify and represent time intervals of the scene that are coherent, thus likely to be dominated by a given source of interest.

@@

\subsection{Methods}

The performance of the temporal scattering transform and the \emph{ob} approaches are assessed in an unsupervised setting (ASSR) and in a supervised setting (ASC).

For ASSR, evaluation is performed on the private part of the DCASE 2013 dataset. The metric used is the precision at rank $k$ ($p@k$), which is computed by taking a query item and counting the number of items of the same class within the $k$ closest neighbors, and then averaging over all query items. The $p@k$ is computed for $k=\lbrace 1,\ldots,9\rbrace$, since each class only has $10$ items. Note that a $p@1$ is equivalent to the classification accuracy obtained by the classifier which chooses the label of the closest neighbor for a given item. For each experimental setting, we only report the results obtained with the sets of parameters, \emph{i.e.} the number of clusters $M$ for the \emph{ob} approaches and the scaling parameter $q$ of the RBF kernels (see Eq. \ref{eq:kc}) leading to the best $p@9$. The \emph{ob} approaches are compared to commonly used early integration approach \emph{early}.

\begin{figure}[t]
\begin{center}
\includegraphics[width=.9\columnwidth]{bw/unsupervised_test1}
\caption{Acoustic scene similarity retrieval (ASSR) in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for scattering coefficients, with and without logarithmic compression, as a function of the rank $k$. \ja{Why not \emph{ob-a} here? Also, the relationship between the different approaches for the regular scattering coefficients seems to be inverted with respect to the log-scattering and the previous figure. That is, here we have \emph{early} $>$ \emph{ob-w} $\approx$ \emph{ob-c} instead of \emph{ob-w} $>$ \emph{ob-w} $>$ \emph{early}.}}
\label{fig:ASS_2}
\end{center}
\end{figure}

For ASC, the systems are again evaluated on the private part of DCASE 2013, but here with five-fold stratified cross validation. The folds are identical to those used in the original challenge. In the same way as the majority of the DCASE 2013 participants, we use an SVM for the ASC task, which is a large-margin binary discriminator with tunable regularization of misclassified examples. The slack parameter $C$ is here set to $1$. Optimal parameters (see above) are this time learned on the public part of the DCASE 2013 dataset, also using five-fold stratified cross validation. \ja{Which parameters are these?} For these experiments, both \emph{early} and \emph{late} integration strategies are evaluated (see Section \ref{sec:eili}).

For the \emph{ob} approaches, we use the precomputed kernels described in Section \ref{sec:object}. For both the \emph{early} and \emph{late} methods, a linear kernel as well as an RBF kernel are used. As with the RBF kernels used in the \emph{ob} approaches, the RBF kernel in the SVM is scaled locally using the method proposed in \cite{selfTuneManor2004}. All feature vectors, that is scattering frames, MFCCs and centroids, are standardized prior to be given to the classifier. The standardization is computed with respect to the train/test splits of the cross validation scheme (see Section \ref{sec:stand}).

@@

\subsection{Acoustic Scene Similarity Retrieval}

This section presents evaluation results for the ASSR settings. The $p@k$ for different settings are shown in Figures \ref{fig:ASS_2} and \ref{fig:ASS_1}, illustrating the effect of the different similarity metrics and the influence of the logarithm, respectively.

@@

Outcomes for the scattering with and without logarithmic compression are shown in Figure \ref{fig:ASS_2}. It can be seen that the logarithmic compression strongly improves the results, especially for the \emph{ob} approaches, which perform worse than \emph{early} without the logarithmic compression.

@@

\subsection{Acoustic Scene Classification}

Surprisingly, although we ran a large number of experiments to formulate the relevance-based quantization scheme into a supervised setting for acoustic scene classification, none managed to outperform the baseline strategy in \emph{late} temporal integration, namely majority voting. Among such methods, the best result is achieved by the \emph{ob-c} approach with log-compressed scattering coefficients, reaching an accuracy of $66\% \pm 7$. \ja{Why don't we display these results?} \ml{I agree, we should put the results} This might be due to the fact that the discriminability gained by the relevance-based quantization approach is already achieved by the classifiers during training and the fact the relevance-based quantization approach is equivalent to an early fusion approach, which in the case of the DCASE 2013 has not been identified as beneficial due to the dataset size (see discussion in Section \ref{sec:eili}). \ja{This sentence is very confusing.}

Logarithmic compression provides a small, albeit consistent boost to acoustic scene classification over all folds in the DCASE 2013 private dataset.
Indeed, as discussed in subsection \ref{sec:logcomp}, and observed in Figure \ref{fig:compression}, the statistical assumption of normality for scattering coefficients is only approximately satisfied once mapped to a logarithmic, decibel-like scale. This transformation improves the discriminative power of the SVMs trained on scattering coefficients, regardless of the chosen temporal integration strategy (early or late) and the inner product kernel (linear or Gaussian RBF).
Again, this is in accordance with our previous findings on acoustic scene similarity retrieval, which are reported in Figure \ref{fig:ASS_2}.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/anden}}]{Joakim And\'en}
received the M.Sc. degree in mathematics from the Universit\'e Pierre et Marie Curie, Paris, France, in 2010 and the PhD degree in applied mathematics from Ecole Polytechnique, Palaiseau, France, in 2014. He is currently a postdoctoral researcher with the Program in Applied and Computational mathematics at Princeton University, Princeton, USA. His research interests include signal processing, machine learning, and statistical data analysis. He is a member of the IEEE.

\end{IEEEbiography}
